Fourmile Calibrations and Output

### 2023-05-15 38HRU_model/fourmile_model_outputs.Rmd
added hru shp, sensor locations, and HRU outputs

<!-- # HRU results -->

<!-- ## Tmean difference -->

<!-- 2011-2020 average of daily station-grid Tmean -->

<!-- ```{r cumulative tmean for HRUs, echo = F} -->
<!-- #grid first -->
<!-- setwd(here("HRU_output/grid")) -->

<!-- read_ages_grid <- function(dataframe){ -->
<!--   read_csv(dataframe, skip = 3) %>% -->
<!--   slice(3:n()) %>% -->
<!--   dplyr::select(-starts_with('@'), -->
<!--                 -1) %>% -->
<!--   mutate(time = ymd(time)) %>% -->
<!--   mutate_if(is.character, as.numeric) %>% -->
<!--   mutate(source = 'grid') -->

<!-- } -->

<!-- #pull in all filenames with HRU in the name -->
<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->

<!-- #read all the csvs using read_ages function -->
<!-- dataframes <- lapply(filenames, read_ages_grid) -->

<!-- #name all the csvs based on first 6 characters -->
<!-- names(dataframes) <- substr(filenames, 1, 6) -->

<!-- #bind all and make 1 df -->
<!-- hru_grids <- dataframes %>% -->
<!--   bind_rows() -->

<!-- #statn next -->
<!-- setwd(here("HRU_output/statn")) -->

<!-- read_ages_statn <- function(dataframe){ -->
<!--   read_csv(dataframe, skip = 3) %>% -->
<!--   slice(3:n()) %>% -->
<!--   dplyr::select(-starts_with('@'), -->
<!--                 -1) %>% -->
<!--   mutate(time = ymd(time)) %>% -->
<!--   mutate_if(is.character, as.numeric) %>% -->
<!--   mutate(source = 'statn') -->

<!-- } -->

<!-- #pull in all filenames with HRU in the name -->
<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->

<!-- #read all the csvs using read_ages function -->
<!-- dataframes <- lapply(filenames, read_ages_statn) -->

<!-- #name all the csvs based on first 6 characters -->
<!-- names(dataframes) <- substr(filenames, 1, 6) -->

<!-- #bind all and make 1 df -->
<!-- hru_statn <- dataframes %>% -->
<!--   bind_rows() -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_tmean <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, tmean)) %>% -->
<!--   rename(tmean_grid = tmean)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(tmean_all_grid = mean(tmean_grid)) -->

<!-- hru_statn_tmean <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, tmean)) %>% -->
<!--   rename(tmean_statn = tmean) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(tmean_all_statn = mean(tmean_statn)) -->

<!-- tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>% -->
<!--   mutate(diff = tmean_all_statn - tmean_all_grid) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_t <- locations %>% -->
<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
<!--                         'Betasso', 'Niwot_Snotel', -->
<!--                         'University Camp SNTL')) -->

<!-- tm_shape(hrus_map_tmean) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ## Tmax difference -->

<!-- ```{r tmax, echo = F} -->

<!-- tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmax_grid') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmax_mean_grid = mean(tmax_grid)) -->

<!-- tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmax_statn') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmax_mean_statn = mean(tmax_statn)) -->

<!-- tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>% -->
<!--   mutate(diff = Tmax_mean_statn - Tmax_mean_grid, -->
<!--          value = as.numeric(value)) -->

<!-- hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- tm_shape(hrus_map_tmax) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ## Tmax monthly average -->

<!-- ```{r tmax month, echo = F} -->

<!-- tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmax_grid') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmax_grid = mean(tmax_grid)) -->

<!-- tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmax_statn') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmax_statn = mean(tmax_statn)) -->

<!-- tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>% -->
<!--   mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid, -->
<!--          value = as.numeric(value)) -->

<!-- tmap_mode('plot') -->

<!-- #march -->
<!-- tmax_hrus_mar<- tmax_hrus_mo %>% -->
<!--   filter(month == 3) -->

<!-- hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value') -->

<!-- mar_tmax <- tm_shape(hrus_map_tmax_mar) + -->
<!--   #tm_polygons('mo_tmax_diff', id = 'value') + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'March avg tmax', -->
<!--             legend.outside = T) -->

<!-- #april -->
<!-- tmax_hrus_apr<- tmax_hrus_mo %>% -->
<!--   filter(month == 4) -->

<!-- hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value') -->

<!-- apr_tmax <- tm_shape(hrus_map_tmax_apr) + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'April avg tmax', -->
<!--             legend.outside = T) -->

<!-- #may -->
<!-- tmax_hrus_may<- tmax_hrus_mo %>% -->
<!--   filter(month == 5) -->

<!-- hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value') -->

<!-- may_tmax <- tm_shape(hrus_map_tmax_may) + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'May avg tmax', -->
<!--             legend.outside = T) -->

<!-- #june -->
<!-- tmax_hrus_jun<- tmax_hrus_mo %>% -->
<!--   filter(month == 6) -->

<!-- hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value') -->

<!-- jun_tmax <- tm_shape(hrus_map_tmax_jun) + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'June avg tmax', -->
<!--             legend.outside = T) -->

<!-- tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax) -->

<!-- ## Tmin difference -->

<!-- ```{r tmin, echo = F} -->

<!-- tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmin_grid') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmin_mean_grid = mean(tmin_grid)) -->

<!-- tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmin_statn') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmin_mean_statn = mean(tmin_statn)) -->

<!-- tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>% -->
<!--   mutate(diff = Tmin_mean_statn - Tmin_mean_grid, -->
<!--          value = as.numeric(value)) -->

<!-- hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- tm_shape(hrus_map_tmin) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ## Tmin monthly average -->

<!-- ```{r tmin month, echo = F} -->
<!-- tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmin_grid') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmin_grid = mean(tmin_grid)) -->

<!-- tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmin_statn') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmin_statn = mean(tmin_statn)) -->

<!-- tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>% -->
<!--   mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid, -->
<!--          value = as.numeric(value)) -->

<!-- tmap_mode('plot') -->

<!-- #march -->
<!-- tmin_hrus_mar<- tmin_hrus_mo %>% -->
<!--   filter(month == 3) -->

<!-- hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value') -->

<!-- mar_tmin <- tm_shape(hrus_map_tmin_mar) + -->
<!--   #tm_polygons('mo_tmin_diff', id = 'value') + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'March avg tmin', -->
<!--             legend.outside = T) -->

<!-- #april -->
<!-- tmin_hrus_apr<- tmin_hrus_mo %>% -->
<!--   filter(month == 4) -->

<!-- hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value') -->

<!-- apr_tmin <- tm_shape(hrus_map_tmin_apr) + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'April avg tmin', -->
<!--             legend.outside = T) -->

<!-- #may -->
<!-- tmin_hrus_may<- tmin_hrus_mo %>% -->
<!--   filter(month == 5) -->

<!-- hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value') -->

<!-- may_tmin <- tm_shape(hrus_map_tmin_may) + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--          breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'May avg tmin', -->
<!--             legend.outside = T) -->

<!-- #june -->
<!-- tmin_hrus_jun<- tmin_hrus_mo %>% -->
<!--   filter(month == 6) -->

<!-- hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value') -->

<!-- jun_tmin <- tm_shape(hrus_map_tmin_jun) + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'June avg tmin', -->
<!--             legend.outside = T) -->

<!-- tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin) -->

<!-- ## Cumulative Precip difference -->

<!-- 2011-2020 average of daily station-grid precip for DOY 365 (or 366) -->

<!-- ```{r cum precip, echo = F} -->
<!-- #get rid of a bunch of data -->
<!-- hru_grid_precip <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, precip)) %>% -->
<!--   rename(precip_grid = precip) -->

<!-- hru_statn_precip <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, precip)) %>% -->
<!--   rename(precip_statn = precip) -->

<!-- precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>% -->
<!--   mutate(diff = precip_statn - precip_grid, -->
<!--          year = year(time)) %>% -->
<!--   group_by(year, ID) %>% -->
<!--   mutate(total_diff = cumsum(diff)) %>% -->
<!--   filter(time == max(time)) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(precip_avg_cumdiff = mean(total_diff)) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_p <- locations %>% -->
<!--   filter(type == 'precip') -->

<!-- tm_shape(hrus_map_precip) + -->
<!--   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') + -->
<!-- tm_shape(locations_p) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ## Solar radiation difference -->

<!-- 2011-2020 average of daily station-grid solar rad -->

<!-- ```{r cum sol rad, echo = F} -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_solrad <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, solRad)) %>% -->
<!--   rename(solrad_grid = solRad)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(solrad_all_grid = mean(solrad_grid)) -->

<!-- hru_statn_solrad <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, solRad)) %>% -->
<!--   rename(solrad_statn = solRad) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(solrad_all_statn = mean(solrad_statn)) -->

<!-- solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>% -->
<!--   mutate(diff = solrad_all_statn - solrad_all_grid) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_solrad <- locations %>% -->
<!--   dplyr::filter(name %in% c('Gordon_South', -->
<!--                         'Betasso', 'Niwot_Snotel')) -->

<!-- tm_shape(hrus_map_solrad) + -->
<!--   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') + -->
<!-- tm_shape(locations_solrad) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ## RH difference -->

<!-- ```{r rh, echo = F} -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_rh <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, rhum)) %>% -->
<!--   rename(rh_grid = rhum)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(rh_all_grid = mean(rh_grid)) -->

>>>>

# HRU results

## Tmean difference

2011-2020 average of daily station-grid Tmean

```{r cumulative tmean for HRUs, echo = F}
hrus <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')

locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/fourmile_sensors.csv')

locations <- locations %>%
  st_as_sf(., coords=c('y','x'), crs = 4326)

#grid first
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/grid_all")

read_ages_grid <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'grid')

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_grid)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_grids <- dataframes %>%
  bind_rows()

#statn next
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/statn_all")

read_ages_statn <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'statn')

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_statn)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_statn <- dataframes %>%
  bind_rows()

#get rid of a bunch of data
hru_grid_tmean <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')

tmap_mode('view')

locations_t <- locations %>%
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel',
                        'University Camp SNTL'))

tm_shape(hrus_map_tmean) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

## Tmax difference

```{r tmax, echo = F}

#get rid of a bunch of data
hru_grid_tmax <- hru_grids %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_grid = tmax)  %>%
  group_by(ID) %>%
  summarize(tmax_all_grid = mean(tmax_grid))

hru_statn_tmax <- hru_statn %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_statn = tmax) %>%
  group_by(ID) %>%
  summarize(tmax_all_statn = mean(tmax_statn))

tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
  rename(value = ID)

hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')

tmap_mode('view')

locations_t <- locations %>%
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel',
                        'University Camp SNTL'))

tm_shape(hrus_map_tmax) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

## Tmin difference

```{r tmin, echo = F}

#get rid of a bunch of data
hru_grid_tmin <- hru_grids %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_grid = tmin)  %>%
  group_by(ID) %>%
  summarize(tmin_all_grid = mean(tmin_grid))

hru_statn_tmin <- hru_statn %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_statn = tmin) %>%
  group_by(ID) %>%
  summarize(tmin_all_statn = mean(tmin_statn))

tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
  rename(value = ID)

hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')

tmap_mode('view')

locations_t <- locations %>%
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel',
                        'University Camp SNTL'))

tm_shape(hrus_map_tmin) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

## Cumulative Precip difference

2011-2020 average of daily station-grid precip for DOY 365 (or 366)

```{r cum precip, echo = F}
#get rid of a bunch of data
hru_grid_precip <- hru_grids %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_grid = precip)

hru_statn_precip <- hru_statn %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_statn = precip)

precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')

tmap_mode('view')

locations_p <- locations %>%
  filter(type == 'precip')

tm_shape(hrus_map_precip) +
  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
tm_shape(locations_p) +
  tm_symbols(col='blue', size=4)

## Solar radiation difference

2011-2020 average of daily station-grid solar rad

```{r cum sol rad, echo = F}

#get rid of a bunch of data
hru_grid_solrad <- hru_grids %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_grid = solRad)  %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad <- hru_statn %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_statn = solRad) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')

tmap_mode('view')

locations_solrad <- locations %>%
  dplyr::filter(name %in% c('Gordon_South',
                        'Betasso', 'Niwot_Snotel'))

tm_shape(hrus_map_solrad) +
  tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
tm_shape(locations_solrad) +
  tm_symbols(col='blue', size=4)

## RH difference

```{r rh, echo = F}

#get rid of a bunch of data
hru_grid_rh <- hru_grids %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_grid = rhum)  %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh <- hru_statn %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_statn = rhum) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')

tmap_mode('view')

locations_rh <- locations %>%
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel'))

tm_shape(hrus_map_rh) +
  tm_polygons('diff', midpoint = NA, id = 'value') +
tm_shape(locations_rh) +
  tm_symbols(col='blue', size=4)

## Average soil sat comparison

```{r soilsat, echo = F}

#get rid of a bunch of data
hru_grid_soilsat <- hru_grids %>%
  dplyr::select(c(time, ID, soilSat)) %>%
  rename(soilsat_grid = soilSat)  %>%
  group_by(ID) %>%
  summarize(soilsat_all_grid = mean(soilsat_grid))

hru_statn_soilsat <- hru_statn %>%
  dplyr::select(c(time, ID, soilSat)) %>%
  rename(soilsat_statn = soilSat) %>%
  group_by(ID) %>%
  summarize(soilsat_all_statn = mean(soilsat_statn))

soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>%
  rename(value = ID)

hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value')

tmap_mode('plot')

soilavg_grid <- tm_shape(hrus_map_soilsat) +
  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average soil sat')

soilavg_statn <- tm_shape(hrus_map_soilsat) +
  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
  tm_legend(legend.outside = T)

tmap_arrange(soilavg_grid, soilavg_statn)

## Average max soil sat comparison

```{r max soilsat, echo = F}

#get rid of a bunch of data
hru_grid_soilsat_max <- hru_grids %>%
  dplyr::select(c(time, ID, soilSat)) %>%
  rename(soilsat_grid = soilSat)  %>%
  mutate(year = year(time)) %>%
  group_by(ID, year) %>%
  summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>%
  summarize(avg_max_grid = mean(soilsat_yrmax_grid))

hru_statn_soilsat_max <- hru_statn %>%
  dplyr::select(c(time, ID, soilSat)) %>%
  rename(soilsat_statn = soilSat) %>%
  mutate(year = year(time)) %>%
  group_by(ID, year) %>%
  summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>%
  summarize(avg_max_statn = mean(soilsat_yrmax_statn))

soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>%
  rename(value = ID)

hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value')

tmap_mode('plot')

soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average max soil sat',
            title.position = c('left', 'top'))

soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
  tm_legend(legend.outside = T)

tmap_arrange(soilavg_grid_max, soilavg_statn_max)

## Average ET comparison

```{r et, echo = F}
#get rid of a bunch of data
hru_grid_ET <- hru_grids %>%
  dplyr::select(c(time, ID, actET)) %>%
  rename(ET_grid = actET)  %>%
  group_by(ID) %>%
  summarize(ET_all_grid = mean(ET_grid))

hru_statn_ET <- hru_statn %>%
  dplyr::select(c(time, ID, actET)) %>%
  rename(ET_statn = actET) %>%
  group_by(ID) %>%
  summarize(ET_all_statn = mean(ET_statn))

ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>%
  rename(value = ID)

hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')

tmap_mode('plot')

ETavg_grid <- tm_shape(hrus_map_ET) +
  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
              breaks = c(0.0,0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average ET')

ETavg_statn <- tm_shape(hrus_map_ET) +
  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
             breaks = c(0.0, 0.1, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
  tm_legend(legend.outside = T)

tmap_arrange(ETavg_grid, ETavg_statn)

## Average ET difference

```{r et diff, echo = F}

ET_hrus <- ET_hrus %>%
  mutate(diff = ET_all_statn - ET_all_grid)

hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')

tmap_mode('plot')

tm_shape(hrus_map_et_diff) +
  tm_polygons('diff', midpoint = NA, id = 'value')  +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average ET difference')

## Average LAI comparison

```{r lai, echo = F}

#get rid of a bunch of data
hru_grid_LAI <- hru_grids %>%
  dplyr::select(c(time, ID, LAI)) %>%
  rename(LAI_grid = LAI)  %>%
  group_by(ID) %>%
  summarize(LAI_all_grid = mean(LAI_grid))

hru_statn_LAI <- hru_statn %>%
  dplyr::select(c(time, ID, LAI)) %>%
  rename(LAI_statn = LAI) %>%
  group_by(ID) %>%
  summarize(LAI_all_statn = mean(LAI_statn))

LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
  rename(value = ID)

hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')

tmap_mode('view')

LAIavg_grid <- tm_shape(hrus_map_LAI) +
  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
              breaks = c(1,2,3,4,5)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average LAI')

LAIavg_statn <- tm_shape(hrus_map_LAI) +
  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
              breaks = c(1,2,3,4,5)) +
  tm_legend(legend.outside = T)

tmap_arrange(LAIavg_grid, LAIavg_statn)
